Case study validations of automatic bullet matching

### 2018-09-28 index.Rmd
phoenix unknown to unknown comparison included

```{r signatures, fig.width = 10, fig.height = 4, fig.cap="Signatures of all six lands of bullets 1 and 2 from barrel 1 of the Hamby set 44."}
# signatures for one bullet
h44cc <- readRDS("data/h44-ccdata.rda")
br1 <- h44cc[1:12]
dframe <- 1:12 %>% purrr::map_df(.f = function(i) {
  d <- br1[[i]]
  d <- d %>% group_by(y) %>% summarize(
    value = mean(value, na.rm=TRUE)
  )
  d$id <- i
  d %>% ungroup(y) %>% rename(
    x = y
  )
})

dframe$bullet <- rep(c("Bullet 1", "Bullet 2"), each = 6)[dframe$id]
dframe$land <- paste("Land", (dframe$id %% 6 + 1))

dframe <- dframe %>% group_by(bullet, land) %>% nest()
names(dframe)[3] <- "ccdata"

library(bulletxtrctr)
dframe <- dframe %>% mutate(
  grooves = ccdata %>% 
    purrr::map(.f = cc_locate_grooves, method = "middle", 
               adjust = 30, return_plot = TRUE)
)
dframe <- dframe %>% mutate(
  sigs = purrr::map2(
    .x = ccdata, .y = grooves, 
    .f = function(x, y) {
      cc_get_signature(
        ccdata = x, grooves = y, span1 = 0.75, span2 = 0.03)
    })
)
dframe$barrelland <- dframe$land
idx <- which(dframe$bullet=="Bullet 2")
dframe$landid <- parse_number(dframe$land)
dframe$landid[idx] <- (dframe$landid[idx] +1) %% 6 + 1
dframe$land <- paste("Land", dframe$landid)

signatures <- dframe %>% select(bullet, land, sigs) %>% tidyr::unnest()
signatures %>% 
  ggplot(aes(x = x/1000)) + 
  geom_line(aes(y = raw_sig), colour = "grey70") +
  geom_line(aes(y = sig), colour = "grey30") +
  facet_grid(bullet~land) +
  ylim(c(-5,5)) +
  theme_bw() +
  ylab("Surface measurement (in microns)") +
  xlab("Relative Location (in millimeters)") 
```

@@

```{r pd, echo=FALSE, fig.width = 10, fig.height=5, fig.cap="Phoenix study: overview of all bullet-to-bullet matches between all pairs of questioned bullets ($y$-axis) and known test fires from ten barrels ($x$ axis). The order of the bullets on the $y$ axis is determined by matching barrel."}
features <- read.csv("data/pd-features.csv.gz")
f2 <- features %>% 
  separate(first, into = c("foo1", "foo2", "barrel1", "bullet1", "land1", "foo3"), remove = FALSE) %>% 
  separate(second, into = c("foo4", "foo5", "bullet2", "land2", "foo6"), remove = FALSE) %>%
  select(-foo1, -foo2, -foo3, -foo4, -foo5, -foo6)

pdnest <- f2 %>% group_by(bullet2, barrel1, bullet1) %>%  nest()

@@

pdnest <- pdnest %>% 
  mutate(
    bullet2 = factor(bullet2, levels=rev(c("N", "B", "E", "T", "H", "J", "K", "Q", "Y", "Z")))
  )
p3 <- pdnest %>%
  ggplot(aes(y = bullet2, x = bullet1, fill = sam_rf)) + 
  geom_tile(size=1) + 
  facet_grid(.~barrel1) +
  ylab("Questioned bullets") + 
  xlab("Known bullets") +
  scale_fill_gradient2("RF score ", low="darkgrey", 
                       high="darkorange", midpoint=0.45, limits=c(0,1)) + 
  scale_colour_manual("same source", values="darkorange") + 
  scale_y_discrete() +
  theme(legend.position="bottom") +
  coord_equal() +
  geom_tile(aes(colour = TRUE), size = .5,
            data = filter(pdnest, KM)) +
  guides(colour = guide_legend(override.aes = list(fill = NA)))

>>>>

```{r signatures, fig.width = 10, fig.height = 4, fig.cap="Signatures of all six lands of bullets 1 and 2 from barrel 1 of the Hamby set 44."}
# signatures for one bullet
# h44cc <- readRDS("data/h44-ccdata.rda")
# br1 <- h44cc[1:12]
# dframe <- 1:12 %>% purrr::map_df(.f = function(i) {
#   d <- br1[[i]]
#   d <- d %>% group_by(y) %>% summarize(
#     value = mean(value, na.rm=TRUE)
#   )
#   d$id <- i
#   d %>% ungroup(y) %>% rename(
#     x = y
#   )
# })
# 
# dframe$bullet <- rep(c("Bullet 1", "Bullet 2"), each = 6)[dframe$id]
# dframe$land <- paste("Land", (dframe$id %% 6 + 1))
# 
# dframe <- dframe %>% group_by(bullet, land) %>% nest()
# names(dframe)[3] <- "ccdata"
# 
# library(bulletxtrctr)
# dframe <- dframe %>% mutate(
#   grooves = ccdata %>% 
#     purrr::map(.f = cc_locate_grooves, method = "middle", 
#                adjust = 30, return_plot = TRUE)
# )
# dframe <- dframe %>% mutate(
#   sigs = purrr::map2(
#     .x = ccdata, .y = grooves, 
#     .f = function(x, y) {
#       cc_get_signature(
#         ccdata = x, grooves = y, span1 = 0.75, span2 = 0.03)
#     })
# )
# dframe$barrelland <- dframe$land
# idx <- which(dframe$bullet=="Bullet 2")
# dframe$landid <- parse_number(dframe$land)
# dframe$landid[idx] <- (dframe$landid[idx] +1) %% 6 + 1
# dframe$land <- paste("Land", dframe$landid)
# signatures <- dframe %>% select(bullet, land, sigs) %>% tidyr::unnest()

signatures <- read.csv("data/signatures.csv")
signatures %>% 
  ggplot(aes(x = x/1000)) + 
  geom_line(aes(y = raw_sig), colour = "grey70") +
  geom_line(aes(y = sig), colour = "grey30") +
  facet_grid(bullet~land) +
  ylim(c(-5,5)) +
  theme_bw() +
  ylab("Surface measurement (in microns)") +
  xlab("Relative Location (in millimeters)") 
```

@@

```{r pd, echo=FALSE, fig.width = 9, fig.height=4, fig.cap="Phoenix study: overview of all bullet-to-bullet matches between all pairs of questioned bullets ($y$-axis) and known test fires from ten barrels ($x$ axis). The order of the bullets on the $y$ axis is determined by matching barrel."}
features <- read.csv("data/pd-features.csv.gz")

f2 <- features %>% 
  separate(first, into = c("foo1", "foo2", "barrel1", "bullet1", "land1", "foo3"), remove = FALSE) %>% 
  separate(second, into = c("foo4", "foo5", "bullet2", "land2", "foo6"), remove = FALSE) %>%
  select(-foo1, -foo2, -foo3, -foo4, -foo5, -foo6)

unknowns <- read.csv("data/pd-features-unknown.csv")
unknowns <- unknowns %>% filter(bullet1 != bullet2)
unknowns <- unknowns %>% mutate(
  bullet2 = gsub("Unknown 1-", "", bullet2),
  bullet1 = gsub("Unknown 1-", "", bullet1)
)
f3 <- rbind(
  f2 %>% select(b1, b2, barrel1, bullet1, 
                land1, bullet2, land2, ccf, rfscore, KM) %>%
    mutate(barrel2 = "Unknown"),
  unknowns %>% select(b1, b2, bullet1, 
                land1, bullet2, land2, ccf, rfscore) %>%
    mutate(barrel1 ="Unknown", barrel2="Unknown", KM=FALSE)
  )
pdnest <- f3 %>% group_by(bullet2, barrel1, bullet1) %>%  nest()

@@

pdnest <- pdnest %>% 
  mutate(
    bullet2 = factor(bullet2, levels=rev(c("N", "B", "E", "T", "H", "J", "K", "Q", "Y", "Z"))),
    bullet1 = factor(bullet1, levels=c("B1", "B2", "B3", rev(levels(bullet2))))
  )
p3 <- pdnest %>%
  ggplot(aes(y = bullet2, x = bullet1, fill = sam_rf)) + 
  geom_tile(size=1) + 
  facet_grid(.~barrel1, scales="free", space="free") +
  ylab("Questioned bullets") + 
  xlab("Known bullets and Questioned bullets") +
  scale_fill_gradient2("RF score ", low="darkgrey", 
                       high="darkorange", midpoint=0.45, limits=c(0,1)) + 
  scale_colour_manual("same source", values="darkorange") + 
  scale_y_discrete() +
  theme_bw() +
  theme(legend.position="bottom") +
#  coord_equal() +
  geom_tile(aes(colour = TRUE), size = .5,
            data = filter(pdnest, KM)) +
  guides(colour = guide_legend(override.aes = list(fill = NA)))
